### 2019-09-13 inst/README.rmd

You can install the most up to date (beta) version easily with
[devtools](https://github.com/hadley/devtools):

```{r eval = FALSE}
install.packages("devtools")
devtools::install_github("ProvTools/Rclean", ref = "dev")
```

Once installed, per usual R practice, just load the *Rclean*:

>>>>

You can install the most up to date version easily with
[devtools](https://github.com/hadley/devtools):

```{r eval = FALSE}
install.packages("devtools")
devtools::install_github("ProvTools/Rclean")
```

Once installed, per usual R practice, just load the *Rclean* package with:
